Figures

### 2018-06-27 code/figures.rmd
Cleaned up figures for publication

I2 <- ggplot(res2, aes(x = z, y = I2)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  xlab("Fisher's z") +
  coord_cartesian(ylim = c(0, 100)) +
  geom_text(x = 0.15, y = 80, label = "b = 69.40, R2 = 0.61", size = 3.5) +
  theme_classic()

@@

H2 <- ggplot(res2, aes(x = z, y = H2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  xlab("Fisher's z") +
  geom_text(x = 0.14, y = 5.9, label = "b = 3.81, R2 = 0.53", size = 3.5) +
  theme_classic()

effect_het <- plot_grid(I2, H2, nrow = 2, labels = c("A", "B"), align = "v") #combine plots
effect_het
# save_plot("../figures/effect_het.png", effect_het,
          # nrow = 2, base_aspect_ratio = 1.3)

@@

dat3 <- dat3 %>% 
  bind_rows(.id = "effect") %>% #create dataframe with identifier
  select(I2, tau, effect) %>% 
  group_by(tau, effect) %>% 
  summarize(I2 = mean(I2)) %>% #Take mean of I2 at each tau-level and for each effect
  ungroup()

#combined line plot gives good overview. Point version of the same is also interesting.
ggplot(dat3, aes(x = tau, y = I2, group = effect)) +
  geom_line(alpha = 0.4) +
  theme_bw() +
  scale_x_continuous(minor_breaks = NULL) +
  scale_y_continuous(minor_breaks = NULL) +
  coord_cartesian(ylim = c(0, 100))

# ggsave("../figures/tau-I2.png")

@@

ggplot(I2_dist, aes(x = I2, group = Heterogeneity, fill = Heterogeneity, linetype = Heterogeneity)) +
  geom_histogram(data = observed, aes(y = ..density.., x = I2), bins = 100, alpha = 1) +
  geom_density(alpha = 0.3) +
  theme_classic() +
  coord_cartesian(xlim = c(0, 100))  +
  scale_fill_brewer(palette = "Dark2", breaks = c("Zero", "Small", "Medium", "Large", "Observed")) +
  scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "solid", "dashed"), breaks = c("Zero", "Small", "Medium", "Large", "Observed")) +
  scale_color_brewer(palette = "Dark2", breaks = c("Zero", "Small", "Medium", "Large", "Observed"))

# ggsave("../figures/density-I2.png")
```

>>>>

I2 <- ggplot(res2, aes(x = z, y = I2)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  xlab("Fisher's z") +
  coord_cartesian(ylim = c(0, 100)) +
  geom_text(x = 0.15, y = 80, label = "b = 69.40, R2 = 0.61", size = 3.5) +
  theme_classic() +
  scale_y_continuous(name = expression(paste(I^2," index", sep = ""))) +
  scale_x_continuous(name = "Effect size (Fisher's z)")

@@

H2 <- ggplot(res2, aes(x = z, y = H2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  xlab("Fisher's z") +
  geom_text(x = 0.14, y = 5.9, label = "b = 3.81, R2 = 0.53", size = 3.5) +
  theme_classic() +
  scale_y_continuous(name = expression(paste(H^2," index", sep = ""))) +
  scale_x_continuous(name = "Effect size (Fisher's z)")

effect_het <- plot_grid(I2, H2, nrow = 2, labels = c("A", "B"), align = "v") #combine plots
effect_het
# save_plot("../figures/effect-het.png", effect_het,
          # nrow = 2, base_aspect_ratio = 1.3, dpi = 600)

@@

OR2d <- c('Allowed vs. forbidden', 'Gain vs. loss framing', 'Norm of reciprocity', 'Low vs. high category scales') #effects that were transformed from OR to SMD

#Categorize effects by type of simulation for graphing
effect_type <- distinct(select(dat, effect, effect_type)) %>% 
  mutate(effect_type = ifelse(effect %in% OR2d | effect_type == "Risk difference" | 
                                effect_type == "Raw mean difference", "MD", effect_type),
         effect_type = recode(effect_type, "d" = 'SMD',
                              "r" = "Fisher's z"))

dat3 <- dat3 %>% 
  bind_rows(.id = "effect") %>% #create dataframe with identifier
  left_join(., effect_type) %>% 
  select(I2, tau, effect, effect_type) %>% 
  group_by(tau, effect, effect_type) %>% 
  summarize(I2 = mean(I2)) %>% #Take mean of I2 at each tau-level and for each effect
  ungroup()

#combined line plot gives good overview. Point version of the same is also interesting.
ggplot(dat3, aes(x = tau, y = I2, group = effect, color = effect_type)) +
  geom_line(alpha = 0.6) +
  theme_bw() +
  scale_x_continuous(name = expression(paste("Between studies standard deviation ", tau)),
                     minor_breaks = NULL) +
  scale_y_continuous(name = expression(paste(I^2," index", sep = "")),
                     minor_breaks = NULL) +
  coord_cartesian(ylim = c(0, 100)) +
  scale_color_brewer(name = "Effect type", palette = "Dark2", 
                     breaks = c("Fisher's z", "MD", "SMD")) +
  theme(legend.position = c(0.8, 0.4),
        legend.background = element_rect(linetype = "solid", color = "black"))

# ggsave("../figures/tau-I2.png", dpi = 600, height =  4 , width = 6.47)

@@

ggplot(I2_dist, aes(x = I2, group = Heterogeneity, fill = Heterogeneity, linetype = Heterogeneity)) +
  geom_histogram(data = observed, aes(y = ..density.., x = I2), bins = 100, alpha = 1) +
  geom_density(alpha = 0.3) +
  theme_classic() +
  coord_cartesian(xlim = c(0, 100))  +
  scale_fill_brewer(palette = "Dark2",
                    breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
                    labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
  scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "solid", "dashed"),
                        breaks = c("Zero", "Small", "Medium", "Large", "Observed"), 
                        labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
  scale_color_brewer(palette = "Dark2", 
                     breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
                     labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
  theme(legend.position = c(0.85, 0.71),
        legend.background = element_rect(linetype = "solid", color = "black")) +
  scale_y_continuous(name = "Density") +
  scale_x_continuous(name = expression(paste(I^2," index", sep = "")))

# ggsave("../figures/density-I2.png", dpi = 600, height =  4 , width = 6.47)
```
